---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# citree

`r badger::badge_devel(color = "blue")`
`r badger::badge_repostatus("Active")`
`r badger::badge_lifecycle("stable")`

The main function of this package is `runCtree()`, which is a wrapper of
[partykit::ctree()](https://rdrr.io/cran/partykit/man/ctree.html) with
addition functions:

-   `partykit::ctree()` only produces the best separation at each node,
    i.e. one tree. By setting `runCtree(recursive = T)`, all trees meeting p-val
    cutoff are produced and can be examined to see which one makes more 
    sense according to domain knowledge. Each round of recursion is done by removing 
    the 1st splitting variable from the input data.frame and running
    `runCtree()`; the recursion stops if no splitting variable is found.
-   The info and stats of each node of each tree are collected and
    summarized in an excel file, which also contains ULRs to each tree.
-   Before running `partykit::ctree()`, low-informative columns and rows
    are removed to reduce computation and adjustment on association
    p-vals.
-   Cases leading to crashes of `partykit::ctree()` are handled, e.g. `Inf` 
    and `-Inf` are converted to `NA` to avoid the following errors:
    " 'breaks' are not unique".

Note:

-   ctree uses `coin::independence_test()` to test the association of
    two variables of any data type. See
    [here](https://cran.r-project.org/web/packages/coin/vignettes/LegoCondInf.pdf)
    for theory behind the test, and
    [here](https://stats.stackexchange.com/questions/404589/ctree-in-r-how-optimal-is-the-optimal-split-point)
    for an explanation of the algorithm, and [here](https://martinschweinberger.github.io/TreesUBonn/) for a nice   tutorial.
-   see
    [here](https://stats.stackexchange.com/questions/12140/conditional-inference-trees-vs-traditional-decision-trees)
    for discussions on the pros and cons of ctree in comparison to other
    trees, e.g. rpart.

See [manual](https://blueskypie.github.io/citree/reference/index.html) and  [examples](https://blueskypie.github.io/citree/articles/citree-vignette.html)

## Installation

Since this is just a toy, I have no plan to submit it to CRAN. So please install 
from github directly:

``` r
devtools::install_github("blueskypie/citree")
```

## Example

```{r, eval = FALSE}
library(citree)
data('mtcars')
re=runCtree(mtcars,'mtcars',oDir='tmp')
```
check the `tmp` directory for output.
