---
title: "citree-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{citree-vignette}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

## Introduction

This is a wrapper of
[partykit::ctree()](https://rdrr.io/cran/partykit/man/ctree.html) with
addition functions:

-   `partykit::ctree()` only produces the best separation at each node,
    i.e. one tree. By setting `recursive = T`, all trees meeting p-val
    cutoff are produced and saved. Recursion is done by removing the 1st
    splitting variable from the input data.frame and running
    `runCtree()` inside `runCtree()`.
-   The info and stats of each node of each tree are collected and
    summarized in an excel file, which also contains ULRs to each tree.
-   Before running `partykit::ctree()`, low-informative columns and rows
    are removed to reduce computation and adjustment on association
    p-vals

Note:

-   ctree uses `coin::independence_test()` to test the association of
    two variables of any data type. See
    [here](https://cran.r-project.org/web/packages/coin/vignettes/LegoCondInf.pdf)
    for theory behind the test, and
    [here](https://stats.stackexchange.com/questions/404589/ctree-in-r-how-optimal-is-the-optimal-split-point)
    for an explanation of the algorithm.
-   see
    [here](https://stats.stackexchange.com/questions/12140/conditional-inference-trees-vs-traditional-decision-trees)
    for discussions on the pros and cons of ctree in comparison to other
    trees, e.g. rpart.


## Example
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, eval = FALSE}
library(citree)
data('mtcars')
re=runCtree(mtcars,'mtcars',oDir='tmp',yi=1,pCut=0.05,naCut=0.3,recursive=T)
```
check the `tmp` directory for output.
